\LARGE How coexistence mechanisms mediate temporal stability

### 2015-03-20 manuscript/manuscript.tex
Fix equations to match R code.

Species richness tends to confer temporal stability of biomass
production in competitive plant communities via compensatory dynamics
among species. Two classes of mechanisms can produce copmensatory
dynamics: (1) temporal complementarity among species and (2) functional
complementarity among species. Temporal complementarity results in
asynchronous population fluctations that, when aggregated over all
populations in a community, dampens variability at the community or
ecosystem level. Such asynchonry in population dynamics through time is
driven by either species-specific responses to variable environmental
conditions or differences in the rate at which species respond to
disturbance.

In contrast to temporal complementarity, functional complementarity
increases community stability by reducing the strength of interspecific
competition. Once thought to be stabilizing at the community level,
recent work suggests interspecific competition is actually
destabilizing. This is because functional complementarity and
competition are negatively correlated, and functional complementarity
among species (i.e., non-temporal niche differences) generally results
in the productivity of spcecies in mixture being greater than expected
from monocultures. So called overyielding increases mean productivity
more than its variance, leading to greater temporal stability.

This implies a strong role for the mode and stability of species
coexistence. Yet, theoretical work aimed toward identifying the
mechanisms by which species richness promotes temporal stability has
treated species coexistence as a foregone conclusion. Most studies
either assume coexistence a priori or ensure coexistence by non-temporal
forms of niche differentiation. In so doing, that large body of work
implicitly assumes that the interaction between environmental
variability and the mechanism(s) by which species coexist is trivial.

@@

\begin{align}
\frac{\text{d}D_{i}}{\text{d}\tau} &= -(m_{D,i}D_{i})\\
\frac{\text{d}N_{i}}{\text{d}\tau} &= f_{i}(R)N_{i} - m_{N,i}N_{i}\\
\frac{\text{d}R_{i}}{\text{d}\tau} &= a(S - R) - \sum\limits_{i=1,2}f_{i}(R)N_{i}
\end{align}

@@

\begin{align}
  V_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)](1-g_{t}) \\
  W_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)]g_{t} \\
  Z_{t+1} &= R(T^-)
\end{align}

>>>>

It is now clear that species richness tends to increase the temporal
stability of biomass production in competitive plant communities. It is
even becoming clear that a few core mechanisms related to compensatory
dynamics among species through temporal or functional complementarity
can explain the positive relationship between diversity and stability.
What remains unclear is how the coexistence mechanism that maintains
species richness influences the strength of compensatory dynamics.
Theoretical studies based on Lotka-Volterra models have given us insight
into the mechanisms that promote stability in communities where species
coexist by fluctuation-independent mechanisms. A remaining challenge is
to explore the importance of proposed mechanisms behind
diversity-stability relationships in communities where species
coexistence is maintained by temporal variability. Specifically, we seek
to understand the mechanisms that promote temporal stability in
communities where species coexistence is achieved because of temporal
variability.

Theory highlights two classes of mechanisms that can stabilize
communities and ecosystems by compensatory dynamics: (1) temporal
complementarity among species and (2) functional complementarity among
species. Temporal complementarity results in asynchronous population
fluctations that, when aggregated over all populations in a community,
dampens variability at the community or ecosystem level. Such asynchonry
in population dynamics through time is driven by either species-specific
responses to variable environmental conditions or differences in the
rate at which species respond to disturbance.

In contrast to temporal complementarity, functional complementarity
increases community stability by reducing the strength of interspecific
competition. Once thought to be stabilizing at the community level,
recent work suggests interspecific competition is actually
destabilizing. This is because functional complementarity and
competition are negatively correlated, and functional complementarity
among species (i.e., non-temporal niche differences) generally results
in the productivity of species in mixture being greater than expected
from monocultures. So called overyielding increases mean productivity
more than its variance, leading to greater temporal stability.

@@

\begin{align}
\frac{\text{d}D_{i}}{\text{d}\tau} &= -(m_{D,i}D_{i})\\
\frac{\text{d}N_{i}}{\text{d}\tau} &= N_{i}[f_{i}(R) - m_{N,i}]\\
\frac{\text{d}R_{i}}{\text{d}\tau} &= - \sum\limits_{i=1,2}f_{i}(R)N_{i}
\end{align}

@@

\begin{align}
  V_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)](1-g_{t}) \\
  W_{i,t+1} &= [N_{i}(T^-)+D_{i}(T^-)]g_{t} \\
  Z_{t+1} &= R(T^-) + R(T^+)
\end{align}
